Sparse Function-space Representation \\ of Neural Networks

### 2023-05-16 paper/main.tex
rewrite 3 points
Sec. 4 and 5

% Short section names etc
% This must be imported last!
%\usepackage{cleveref}
\usepackage[capitalise,nameinlink]{cleveref}
\crefname{section}{Sec.}{Secs.}
\crefname{algorithm}{Alg.}{Algs.}
\crefname{appendix}{App.}{Apps.}
\crefname{definition}{Def.}{Defs.}
\crefname{table}{Tab.}{Tabs}

@@

\section{Sparse function-space sequential learning}
\label{sec:sequential}
%
We have presented a method for converting any trained neural network into a sparse function-space representation.
In this section, we demonstrate how sequential learning methods can benefit from our function-space representation and it's associated uncertainty estimates.

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks. However, they are limited to use subset approximations of the posterior.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from
At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points. Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows, 
%
\begin{equation}\textstyle
 	\bar{\MB}^{-1}_t = \MKzz^{-1} \MBeta_\vu \MKzz^{-1} \in \R^{M \times M}, 
 	\quad \text{s.t.} \quad
 	\MBeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 	% \quad \forall t \in [1, T]
\end{equation}
%
where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\MZ_t = \{\vz_i\}_{i=1}^M$ for task $t$ .
%
We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{M}$ are the neural network outputs associated to them, computed with the MAP estimate $\weights_t^*$ after task $t$. Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$\textsuperscript{th} entry is $f_{\weights_t^*}(\vz_i)\in \R$. Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.

@@

\section{Experiments}
\label{sec:experiments}

\todo{Overview of experiments}

Our experiments seek to answer the following questions:
\begin{enumerate}
  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations? Does our method's ability to consider the full data set offer benefits over subset function-space methods?
  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
  \item \textbf{Function-space updates} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? Are they as good as retraining from scratch?
  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
\end{enumerate}

\subsection{Capturing uncertainty in UCI tasks under supervised learning}
%

@@

\subsection{Updating the  network representation for Continual learning}
%% Very rough draft
This experiment's section is meant to demonstrate the quality of our sparse representation to retain previous knowledge in the Continual learning setting. Unfortunately the CL literature is based on methods that require very diverse set of hyperparameters 
% Idea: it is very difficult to have everything under control, because model changes, settings change, optimizer change, and so on. Then what we did was trying to replicate as close as possible the results for the competing methods by using their codebases where available and choosing the hyperpameters accordingly to their choices.

@@

\subsection{Reinforcement learning}
% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
% Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
% Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
% hope to discover new high reward actions (exploration)?

>>>>

% Short section names etc
% This must be imported last!
%\usepackage{cleveref}
\usepackage[capitalise,nameinlink]{cleveref}
\crefname{section}{Sec.}{Secs.}
\crefname{algorithm}{Alg.}{Algs.}
\crefname{appendix}{App.}{Apps.}
\crefname{definition}{Def.}{Defs.}
\crefname{table}{Table}{Tables}

@@

\section{Maintaining a sparse function-space representation in sequential learning}
\label{sec:sequential}
%
We have presented a method for converting any trained neural network into a sparse function-space representation. The sparse representation opens an avenue for maintaining (and updating) a representation of the neural network, an important feature for sequential learning, such as continual learning.\looseness-1
%In this section, we demonstrate how sequential learning methods can benefit from our function-space representation and it's associated uncertainty estimates.

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks. However, they are limited to use subset approximations of the posterior.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from
At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points. Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows, 
%
\begin{equation}\textstyle
 	\bar{\MB}^{-1}_t = \MKzz^{-1} \MBeta_\vu \MKzz^{-1} \in \R^{M \times M}, 
 	\quad \text{s.t.} \quad
 	\MBeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 	% \quad \forall t \in [1, T]
\end{equation}
%
where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\MZ_t = \{\vz_i\}_{i=1}^M$ for task $t$ .
%
We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{M}$ are the neural network outputs associated to them, computed with the MAP estimate $\weights_t^*$ after task $t$. Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$\textsuperscript{th} entry is $f_{\weights_t^*}(\vz_i)\in \R$. Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.

@@

\section{Experiments}
\label{sec:experiments}
%
We present a series of experiments designed to demonstrate the versatility and efficacy of our proposed \our framework. We seek to find answers to the following questions: 
\textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods? (\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations? 
\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? Are they as good as retraining from scratch? \todo{what do we have on this?}
\textbf{Representation:} Can a sparse function-space representation help retain knowlegde from previous tasks in CL? (\cref{sec:cl-exp})
\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL under sparse rewards? (\cref{sec:rl-exp})

%Initially, we explore the capability of our method to capture predictive uncertainty through supervised learning tasks using UCI datasets. Subsequently, we extend our supervised learning experiment to image datasets, demonstrating our method's robustness and adaptability to more complex, high-dimensional data. Next, we investigate the potential of our method in a continual learning context, where we update the neural network representation in response to incoming data without necessitating retraining. Lastly, we delve into the realm of reinforcement learning to ascertain the applicability of our approach in an environment that requires sequential decision-making. Each experiment is designed to illuminate a different facet of our method, thereby exemplifying its broad range of applicability and potential for future utilization.

%
%Our experiments seek to answer the following questions:
%\begin{enumerate}
%  \item \textbf{Predictions:} How do predictions with our sparse function-space approximation compare to weight-space approximations? Does our method's ability to consider the full data set offer benefits over subset function-space methods?
%  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
%  \item \textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? Are they as good as retraining from scratch?
%  \item \textbf{Uncertainty:} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
%  \item \textbf{Representation:} Is our sparse function-space representation useful for continual learning?
%\end{enumerate}

\subsection{Capturing uncertainty in UCI tasks under supervised learning}
\label{sec:uci}
%

@@

\subsection{Updating the  network representation in continual learning}
%% Very rough draft
This experiment's section is meant to demonstrate the quality of our sparse representation to retain previous knowledge in the Continual learning setting. Unfortunately the CL literature is based on methods that require very diverse set of hyperparameters 
% Idea: it is very difficult to have everything under control, because model changes, settings change, optimizer change, and so on. Then what we did was trying to replicate as close as possible the results for the competing methods by using their codebases where available and choosing the hyperpameters accordingly to their choices.

@@

\subsection{Reinforcement learning under sparse rewards}
\label{sec:rl-exp}
% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
% Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
% Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
% hope to discover new high reward actions (exploration)?
